### 2022-09-09 Thesis/text/einleitung.tex
state of the art

@@

Description of the Problem

Robots regurlarly needs operator in case smth unexpected happens\\

this may include: unexpected collisions, a system restart is needed, battery is empty\\

The system is not able to react and handle unforeseen situations\\

This can lead to safety issues during the operation of a robot. These safety issues can lead to uncontrolled driving maneuvers due to wrong sensor data or a wrong environment represantation.\\

Due to the need of the robot to require an operator, the robot is closer to an automated instead of an autonomous vehicle. 
Difference is defined by the SAE Levels for automonous driving in cars.\\

It is important for the robot to possess the ability to navigate in an uncertain environment to guarantee the safety of the robot itself and all other actors in its environment, these can be other robots and humans.\\

@@

This thesis proposes a comprehensive approach for behavior planning for an autonomous mobile robot.

\textbf{How can behavior planning increase the safety and autonomy of an autonomous mobile robot running ROS?}

>>>>

Research question:
\textbf{How can behavior planning increase the robustness and autonomy of a robot running ROS2?}

@@

Description of the Problem:

Despite the advancements in autonomous driving the robot regurlarly needs an operator in case smth unexpected happens.

This may include: unexpected collisions, a system restart is needed, battery is empty, the environment is too crowded and the robot gets stuck

The system is not able to react and handle unforeseen situations.

This can lead to safety issues during the operation of a robot. These safety issues can lead to uncontrolled driving maneuvers due to wrong sensor data or a wrong environment represantation.

Due to the need of the robot to require an operator for safe, the robot is not really autonomous despite it being labeled as such.

(Difference is defined by the SAE Levels for automonous driving in cars.) \\

Relevance, need for research:\\
It is important for the robot to possess the ability to navigate in an uncertain environment to guarantee the safety of the robot itself and all other actors in its environment, these can be other robots and humans.\\

@@

Planned solution:\\

This thesis will explore an approach how an extension of the current software architecture and behavior planning capabilities for an autonomous mobile robot that is running ROS2 can improve the autonomy of the robot.

Expected results:\\

The desired outcomes of these implemented extension will be an increase of robustness and decrease of required human actions during a number of scenarios. In these scenarios, failures and and problems are artificially induced to test the robots abilities to behave autonomously.

\textit{Research gap is not named so far}
